The Key to a Data Parallel Compiler

### 2016-04-07 2016-spring-array/2016-array-key.tex
Add in references to Co-dfns in other places

In the following sections we describe the core methods and idioms surrounding 
the AST encoding, construction of the Node Coordinate Matrix, and the use 
of these structures in handling nested, recursive AST relationships. This 
enables us to perform arbitrary computation over arbitrary sub-trees of an 
AST selected by parent-child relationships in the manner often seen in 
compiler transformations. These ideas have been further implemented and tested 
through the implementation of a complete data-parallel by construction 
compiler, called Co-dfns, that compiles a lexically scoped, functionally 
oriented dialect of APL with nested functions. The compiler targets both the 
GPU and the CPU, and its core compiler is implemented in this pure, restricted 
language that uses only function composition over data-parallel primitives.

@@

The Co-dfns compiler is an experimental commercial compiler funded by 
Dyalog, Ltd. It is intended to provide increased scaling and performance
for APL programmers using the dfns syntax (lexically scoped, functionally 
oriented APL). These techniques form one of the foundational elements to 
the architecture of the compiler, which is built in the style of a Nanopass 
compiler, with very small passes chained together through composition, with 
the added requirements that each compiler pass must be fully data parallel.

>>>>

In the following sections we describe the core methods and idioms surrounding 
the AST encoding, construction of the Node Coordinate Matrix, and the use 
of these structures in handling nested, recursive AST relationships. This 
enables us to perform arbitrary computation over arbitrary sub-trees of an 
AST selected by parent-child relationships in the manner often seen in 
compiler transformations. These ideas have been further implemented and tested 
through the implementation of a complete data-parallel by construction 
compiler, called Co-dfns, that compiles a lexically scoped, functionally 
oriented dialect of APL with nested functions. 
\cite{hsu2014co,hsu2015accelerating}
The compiler targets both the
GPU and the CPU, and its core compiler is implemented in this pure, restricted 
language that uses only function composition over data-parallel primitives.

@@

The Co-dfns compiler is an experimental commercial compiler funded by 
Dyalog, Ltd. \cite{hsu2014co,hsu2015accelerating}
It is intended to provide increased scaling and performance
for APL programmers using the dfns syntax (lexically scoped, functionally 
oriented APL). These techniques form one of the foundational elements to 
the architecture of the compiler, which is built in the style of a Nanopass 
compiler, with very small passes chained together through composition, with 
the added requirements that each compiler pass must be fully data parallel.
